[dcpo_demsupport] Appendix

### 2020-07-12 paper/dcpo_demsupport.Rmd
clean up
address #3, uncertainty embedded.

```{r country_years}
dcpo_input_cy <- dcpo_input_raw1 %>% 
  dplyr::select(country, year) %>% 
  unique()

save(dcpo_input_cy, file = here::here("data", "dcpo_input_cy.rda"))
```

@@

>>>>

@@

```{r country_years}
path_df <-
  list.files(
    "../data",
    pattern = ".*_theta.rda",
    recursive = TRUE,
    full.names = TRUE
  ) %>%
  .[str_which(., "claassen")]

load(path_df)

df_thetaDraw <- map_df(seq(claassen_m5_theta$theta[1, , 1]),
       function(year) {
         map_df(seq(claassen_m5_theta$theta[1, 1, ]),
                function(country) {
                  df_temp <-
                    sample(claassen_m5_theta$theta[, year, country],
                           size = 100,
                           replace = TRUE) %>%
                    matrix(ncol = 100) %>%
                    as_tibble()
                  df_temp$yearID <- year
                  df_temp$countryID <- country
                  return(df_temp)
                })
       }) %>% 
  pivot_longer(
    df_temp,
    cols = starts_with("V"),
    names_to = "draw",
    values_to = "theta"
  ) %>% 
  group_split(draw)
```

### 2020-07-12 paper/dcpo_demsupport_appendix.Rmd
address #3, uncertainty embedded.

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse # data wrangling
)

@@

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  plm,
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse # data wrangling
)

@@

```{r claassenWUncertainty}
load("../data/claassen_replication_input.rda")
load("../data/claassen_m5_theta.rda")

ls_year <- 1988:2017
ls_country <- claassen_replication_input$data$country %>% unique

df_thetaDraw <- map_df(seq(ls_year), # year2
       function(oneYear) {
         map_df(seq(ls_country),
                function(oneCountry) {
                  df_temp <-
                    sample(claassen_m5_theta$theta[, oneYear, oneCountry],
                           size = 100, #draw 100 from the distribution
                           replace = TRUE) %>%
                    matrix(ncol = 100) %>%
                    as_tibble()
                  df_temp$year <- ls_year[oneYear]
                  df_temp$country <- ls_country[oneCountry]
                  return(df_temp)
                })
       }) %>% 
  pivot_longer(
    cols = starts_with("V"),
    names_to = "draw",
    values_to = "theta"
  ) %>% 
  group_split(draw)

df_controls <- read_csv("../data/Support_democracy_ajps.csv")

df_thetaDraw <- map(df_thetaDraw, function(oneDraw){
  left_join(oneDraw, df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
    pdata.frame(index = c("country", "year"))
})

result_m5O <- plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(SupDem_trim, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), pdata.frame(df_controls, index = c("Country", "Year")), model="pooling")

result_m5N <- map(df_thetaDraw, function(aDataset){
  plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
})

vcovBK_se <- function(x){
  vcovBK(x, cluster = "time") %>% 
    sqrt(diag(.))}

result_betas_m5 <- MIextract(result_m5, fun = coef)
result_vars_m5 <- MIextract(result_m5, fun = vcovBK_time)

summary(result_m5O)
summary(MIcombine(results = result_betas_m5, 
                  variance = result_vars_m5))
```
